FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2017-10-19 NewVersion/sections/Overview.tex
small fix. to 25pages

\section{A Running Example: Drawable Deck}~\label{sec:overview}
This section illustrates the problem of unintentional method conflicts,
together with the features of our model on addressing this issue, by
a simple running example. In the following text we will introduce three
problems one by one and have a discussion on possible workarounds and
our solutions.
Problems 1 and 2 are related to hierarchical dispatching, and in 
C++ it is possible to have similar solutions to both
problems. Hence it is important to emphasize that, with respect to
hierarchical dispatching, our model is not a novel
mechanism. Instead, 
inspired by the C++ solutions, our contribution is formalizing a minimal calculus
of this feature together with a proof of type soundness. However, for the final problem, there is no satisfactory approach
in existing languages, thus what we propose is a new feature (hierarchical
overriding) with the corresponding formalization of that feature.

@@

interface Drawable {
  void draw() { // draws something on the screen
    JFrame frame = new JFrame();
    frame.setVisible(true);
  }
}
\end{lstlisting}\vspace{3pt}
In \lstinline|Deck|,
\lstinline|draw| uses \lstinline|println|, which is a
library function. 
The two \lstinline|draw| methods can have different return types, but for simplicity, 
they both return \lstinline|void| here. Note that, similarly to
Featherweight Java~\cite{Igarashi01FJ}, \lstinline|void| is
unsupported in our formalization. We could have also defined an interface called \lstinline|Void|
and return an object of that type instead. To be concise, however, we
use \lstinline|void| in our examples.
For \lstinline|Drawable| the \lstinline|draw| method
creates a blank canvas.

>>>>

\section{A Running Example: Drawable Deck}~\label{sec:overview}
This section illustrates the problem of unintentional method conflicts,
together with the features of our model on addressing this issue, by
a simple running example. In the following text we will introduce three
problems one by one and have a discussion on possible workarounds and
our solutions.
Problems 1 and 2 are related to hierarchical dispatching, and in 
C++ it is possible to have similar solutions to both
problems. Hence it is important to emphasize that, with respect to
hierarchical dispatching, our model is not a novel
mechanism. Instead, 
inspired by the C++ solutions, our contribution is formalizing a minimal calculus
of this feature together with a proof of type soundness. However, for the final problem, there is no satisfactory approach
in existing languages, thus what we propose is a novel feature (hierarchical
overriding) with the corresponding formalization of that feature.

@@

interface Drawable {
  void draw() { // draws something on the screen
    JFrame frame = new JFrame();
    frame.setVisible(true);
  }
}
\end{lstlisting}\vspace{3pt}
In \lstinline|Deck|,
\lstinline|draw| uses \lstinline|println|, which is a
library function. 
The two \lstinline|draw| methods can have different return types, but for simplicity, 
the return types are both \lstinline|void| here. Note that, similarly to
Featherweight Java~\cite{Igarashi01FJ}, \lstinline|void| is
unsupported in our formalization. We could have also defined an interface called \lstinline|Void|
and return an object of that type instead. To be concise, however, we
use \lstinline|void| in our examples.
In interface \lstinline|Drawable|, the \lstinline|draw| method
creates a blank canvas.
